High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-03-20 notebooks/intro.qmd
setting up notebooks

```{julia}
using CCE
using CCE: set_size_penalty, distance_from_energy, distance_from_targets
using ConformalPrediction
using CounterfactualExplanations
using CounterfactualExplanations.Data
using CounterfactualExplanations.Objectives
using Distributions
using Flux
using JointEnergyModels
using LinearAlgebra
using MLJBase
using MLJFlux
using Plots
img_height = 300
```

@@

@@

```{julia}
M = CCE.ConformalModel(conf_model, mach.fitresult)
x = select_factual(counterfactual_data,rand(1:size(counterfactual_data.X,2)))
y_factual = predict_label(M, counterfactual_data, x)[1]
target = counterfactual_data.y_levels[counterfactual_data.y_levels .!= y_factual][1]
```

@@

```{julia}
M = CCE.ConformalModel(conf_model, mach.fitresult; likelihood=:classification_multi)
x = select_factual(counterfactual_data,rand(1:size(counterfactual_data.X,2)))
y_factual = predict_label(M, counterfactual_data, x)[1]
target = counterfactual_data.y_levels[counterfactual_data.y_levels .!= y_factual][1]
```

>>>>

```{julia}
include("notebooks/setup.jl")
eval(setup_notebooks)
```

@@

M = CCE.ConformalModel(conf_model, mach.fitresult)

@@

```{julia}
x = select_factual(counterfactual_data,rand(1:size(counterfactual_data.X,2)))
y_factual = predict_label(M, counterfactual_data, x)[1]
target = counterfactual_data.y_levels[counterfactual_data.y_levels .!= y_factual][1]
```

@@

niter = 100
nsamples = 100
M = CCE.ConformalModel(conf_model, mach.fitresult; likelihood=:classification_multi)

plts = []
for target ∈ counterfactual_data.y_levels
    sampler = CCE.EnergySampler(M, counterfactual_data, target; niter=niter, nsamples=100)
    Xgen = rand(sampler, nsamples)
    plt = plot(M, counterfactual_data; target=target, zoom=-0.5,cbar=false)
    scatter!(Xgen[1,:],Xgen[2,:],alpha=0.5,color=target,shape=:star,label="X|y=$target")
    push!(plts, plt)
end
plot(plts..., layout=(1,length(plts)), size=(img_height*length(plts),img_height))
```

```{julia}

x = select_factual(counterfactual_data,rand(1:size(counterfactual_data.X,2)))
y_factual = predict_label(M, counterfactual_data, x)[1]
target = counterfactual_data.y_levels[counterfactual_data.y_levels .!= y_factual][1]
```

### 2023-03-20 notebooks/proposal.qmd
setting up notebooks

```{julia}
using CounterfactualExplanations
using CounterfactualExplanations.Data: load_mnist
using CounterfactualExplanations.Models: load_mnist_mlp
using Images
using MLDatasets
using MLDatasets: convert2image
using Plots
www_path = "dev/www"
```

>>>>

```{julia}
include("notebooks/setup.jl")
eval(setup_notebooks)
```
